### 2016-12-01 thesis/intro/intro.tex
finished draft for the cancer part of the intro

>>>>

Traditionally, the treatment of cancer has been surgery, radiation therapy and chemotherapy.
Though surgery is an effective method to remove the tumour from the patient, there is always a risk of metastasis and recurrence, which is why combination of surgery with other treatments like chemotherapy is usually considered.
Earlier chemotherapeutic drugs and radiation therapy had limited effect on tumours due to their resistance against these treatments \citep{Wilhelm2006}.
However, greater understanding of the pathways and mechanisms that tumour cells use have shed  light on the development of drugs that are more effective against tumours.
RAF inhibitors are among one of many.

The RAS-RAF-MEK-ERK signalling pathway is a pathway involved in cell survival, growth and proliferation \citep{Samatar2014,Wilhelm2006}.
The members of this pathway are often mutated in many types of cancers, causing an overactivation of this pathway.
For example, approximately a third of cancers contain a mutation in the RAS oncogene which allows the constitutive activation of the RAS-ERK pathway \citep{Samatar2014}.
Development of the drugs that target  the downstream RAF and its mutant forms (such as BRAF$^{V600E}$) have been successful, and many RAF inhibitor drugs such as sorafenib and vemurafenib have been approved for use clinically \citep{Samatar2014,Wilhelm2006}.
Even though our understandings of signalling pathways and drug development based on these knowledge is improving, there is always the possibility of tumour to acquire resistance to those drugs and there is always a need for new ways to treat cancer patients \citep{Samatar2014}.

In fact, there has been evidence of pathway cross-talks between RAS-ERK pathway and \gls{pi3k}/Akt pathway \citep{Moelling2002,Zimmermann1999a}.
Furthermore, a study in \textit{Drosophila} showed that the inhibition of just a single pathway does not necessarily stop the effect of the pathway, as the signal can flow through alternate pathways \citep{Dar2012}.
Pathway cross-talk and increased flux through alternate pathways could be one of the ways in which tumour cells acquire resistance to drugs.
However, the effectiveness of targeting multiple pathways in humans is yet to be confirmed and further investigations are required to solidify the mode of action and its relevance to tumour biology.
\\

\noindent
Though there are difficulties such as resistance to drugs and metastasis, further development of technologies and improved knowledge of tumour biology will only get us closer to the cure of cancer.
